\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{Bibliografia}

\bibitem{context}
Towards a Better Understanding of Context and Context-Awareness
\author{Anind K. Dey, Gregory D. Abowd}
\url{ftp://ftp.cc.gatech.edu/pub/gvu/tr/1999/99-22.pdf}

\bibitem{gps}
Sistema di posizionamento globale
\url{https://it.wikipedia.org/wiki/Sistema_di_posizionamento_globale#cite_note-1}


\bibitem{IPS}
Indoor positioning system
\url{https://en.wikipedia.org/wiki/Indoor_positioning_system}

\bibitem{IPS2}
Progettazione e realizzazione di un Indoor Positioning System basato su geomagnetismo e sensor fusion
\url{http://amslaurea.unibo.it/12840/1/federico_torsello_tesi.pdf}

\bibitem{alg1}
Luca Pappalardo, "Localizzazione - Problema, Tecniche, Algoritmi - Reti mobili:
Ad Hoc e di sensori", 2011,
\url{http://didawiki.di.unipi.it/lib/exe/fetch.php/rhs/localizzazione.pdf}

\bibitem{alg2}
Cuccado, De Franceschi, Fauri, Sartor, "Analisi di algoritmi di autolocalizzazione
per reti di sensori wireless", 2007,
\url{https://art.torvergata.it/retrieve/handle/2108/773/6945/Paolo-Sperandio-Tesi-PhD.pdf}

\bibitem{indoorThesis}
An adaptive indoor positioning system based on Bluetooth Low Energy RSSI
\author{Nicola Cinefra}
\url{https://www.politesi.polimi.it/bitstream/10589/92284/3/NicolaCinefra770910TesiDefinitiva.pdf}

\bibitem{market}
Harrop P, Raghu D. Mobile Phone Indoor Positioning Systems (IPS) and Real Time
Locating Systems (RTLS) 2014-2024. Forecasts, Players, Opportunities. IDTechEx



\bibitem{rssi}
Ugur Bekcibasi, "Increasing RSSI Localization Accuracy with Distance Reference
Anchor in Wireless Sensor Networks", 2014,
\url{http://www.uni-obuda.hu/journal/Bekcibasi_Tenruh_54.pdf}

\bibitem{toaProblem}
Mak LC, Furukawa T. A ToA-based Approach to NLOS Localization Usiong Low-Frequency Sound. ACRA2006 (Auckland, New Zealand); 2006


\bibitem{aoa}
A Simple Technique for angle of arrival measurement
\url{https://www.researchgate.net/publication/4368716_A_Simple_Technique_for_angle_of_arrival_measurement}

\bibitem{triangolazione}
Generalized Geometric Triangulation Algorithm for Mobile Robot
Absolute Self-Localization 
\url{https://pdfs.semanticscholar.org/dee6/fb124433cac10744afd9502b165ffdecb202.pdf}

\bibitem{sensorfusion}
Sensor fusion
\url{https://en.wikipedia.org/wiki/Sensor_fusion}

\bibitem{mems}
Jeroen Hol "Sensor Fusion and Calibration of
Inertial Sensors, Vision,
Ultra-Wideband and GPS"
\url{https://www.xsens.com/wp-content/uploads/2014/pdf/Hol2011%20-%20Dissertation.pdf}

\bibitem{principimems}
Janusz Bryzek "Principles of MEMS"
\url{https://www.wiley.com/legacy/wileychi/hbmsd/pdfs/mm573.pdf}


\bibitem{acc}
MEMS Accelerometer
\url{http://www.instrumentationtoday.com/mems-accelerometer/2011/08/}


\bibitem{gyromodel}
H. Titterton and J. L. Weston. Strapdown inertial navigation technology. IEE
radar, sonar, navigation and avionics series. Peter Peregrinus Ltd., Stevenage,
UK, 1997. ISBN 0863413587.

\bibitem{corolois}
Forza di Coriolis, Wikipedia
\url{https://it.wikipedia.org/wiki/Forza_di_Coriolis}

\bibitem{gyroMems}
The Development of Micromachined Gyroscope Structure and
Circuitry Technology, Dunzhu Xia, Cheng Yu and Lun Kong

\bibitem{assetto}
TECNICHE DI STIMA E CONTROLLO DI ASSETTO DI
SATELLITI. Andrea Fagiani. 
\url{http://control.disp.uniroma2.it/carnevale/archivio/Tesi/andreafagianiM/tesi.pdf}

\bibitem{assetto2}
DETERMINAZIONE D'ASSETTO MEDIANTE
IL FILTRO DI KALMAN ESTESO
MOLTIPLICATIVO. Fabio Cisaria. 

\bibitem{wikiRoll}
Aircraft principal axes, Wikipedia.
\url{https://en.wikipedia.org/wiki/Aircraft_principal_axes}

\bibitem{gimbal}
Gimbal lock, Wikipedia.
\url{https://en.wikipedia.org/wiki/Gimbal_lock}

\bibitem{trackingThesis}
Advanced algorithms and architectures for MEMS inertial sensor platforms 
in orientation tracking and in fall detection applications. Simone Sabatelli.
Università di Pisa.

\bibitem{motion}
MotionFX middleware library in X-CUBE-MEMS1 software
expansion for STM32Cube.\\
\url{http://www.st.com/content/ccc/resource/technical/document/user_manual/group0/31/0e/66/39/cb/f7/4e/cd/DM00394369/files/DM00394369.pdf/jcr:content/translations/en.DM00394369.pdf}

\bibitem{kalmanWiki}
Filtro di Kalman, Wikipedia.\\
\url{https://it.wikipedia.org/wiki/Filtro_di_Kalman}

\bibitem{i2cWiki}
I2C, Wikipedia.\\
\url{https://it.wikipedia.org/wiki/I%C2%B2C}
	
\bibitem{hal}
Description of STM32F4 HAL and LL drivers.\\
\url{https://www.st.com/content/ccc/resource/technical/document/user_manual/2f/71/ba/b8/75/54/47/cf/DM00105879.pdf/files/DM00105879.pdf/jcr:content/translations/en.DM00105879.pdf}

\bibitem{usbCDC}
Universal Serial Bus Class Definitions for Communication Devices.\\
\url{https://cscott.net/usb_dev/data/devclass/usbcdc11.pdf}

\bibitem{usbCDC2}
CDC Class Overview.\\
\url{https://doc.micrium.com/display/DOC/CDC+Class+Overview}

\end{thebibliography}



